---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SILViA

<!-- badges: start -->
<!-- badges: end -->

The goal of SILViA is to provide a method to identify outlying points recorded by a CTD device along a depth profile, which are not congruent with the range of measurements taken in the surrounding water column. These are labeled as "incongruent" points.
For this, the package includes a function to import and format .vp2 files, as well as functions to visualize depth profiles and the incongruent points they contain. 

## Installation

You can install the development version of SILViA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("KemenesT/SILViA")
```

## Usage

A fairly common task when dealing with strings is the need to split a single string into many parts.
This is what `base::strplit()` and `stringr::str_split()` do.

```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

Notice how the return value is a **list** of length one, where the first element holds the character vector of parts.
Often the shape of this output is inconvenient, i.e. we want the un-listed version.

That's exactly what `regexcite::str_split_one()` does.

You can also embed plots, for example:
```{r pressure, echo = FALSE}

```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
