---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SILViA

<!-- badges: start -->
<!-- badges: end -->

The goal of SILViA is to provide a method to identify outlying points recorded by a CTD device along a depth profile, which are not congruent with the range of measurements taken in the surrounding water column. These are labeled as "incongruent" points.
For this, the package includes a function to import and format .vp2 files, as well as functions to visualize depth profiles and the incongruent points they contain. 

## Installation

You can install the development version of SILViA like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SILViA)
## basic example code
```

You can also embed plots, for example:
```{r pressure, echo = FALSE}
plot(pressure)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
